The Driving Forces of API Evolution

### 2015-05-21 thesis/paper.tex
title+author
Another update

\title{The Driving Forces Behind API Evolution}

@@

\author{
% 1st. author
\alignauthor
John Burchell\\
%       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
%       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{william.granli@gmail.com}
%\and
% 3rd. author
%\alignauthor Imed Hammouda\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
%       \affaddr{University of Gothenburg}\\
%       \email{imed.hammouda@gu.se}
% 4th 
%\alignauthor Eric Knauss\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
%       \affaddr{University of Gothenburg}\\
%       \email{imed.hammouda@gu.se}
}

@@

%Background and need for study, make it interesting

%Other studies
Other studies have investigated why changes occur to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of the API according to software evolution theories. Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
% How do we do it?
Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
% Our results and future suggestions
The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality. It highlighted the fact that not all software evolution theories are applicable to APIs. We found that changes happen sporadically rather than slowly over time and the contradiction of a software evolution law that states the opposite is true. The research further supported the importance of a feedback loop of a software system, which is something that company A also wants. The study concludes by proposing suggestions for future studies based on our findings.

>>>>

\title{The Driving Forces of API Evolution}

@@

\author{
% 1st. author
\alignauthor
John Burchell\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{william.granli@gmail.com}
%\and
% 3rd. author
%\alignauthor Imed Hammouda\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
%       \affaddr{University of Gothenburg}\\
%       \email{imed.hammouda@gu.se}
% 4th 
%\alignauthor Eric Knauss\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
%       \affaddr{University of Gothenburg}\\
%       \email{imed.hammouda@gu.se}
}

@@

%Background and need for study, make it interesting
Evolving a software system is a precipitous activity. Many software evolution theories have been created to assist changing systems, however, as modern systems make greater use of APIs, a question must be asked: do these theories apply to the evolution of APIs? (!!!what is driving the evolution of APIs? - Might fit better with the title?)
%Other studies
Studies have investigated why changes are made to APIs and how these changes affect systems, but they do not attempt to understand the driving forces behind the evolution of an API, according to software evolution theories. Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
% How do we do it?
Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
% Our results and future suggestions
The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality. It highlighted the fact that not all software evolution theories are applicable to APIs. We found that changes happen sporadically rather than slowly over time and the contradiction of a software evolution law that states the opposite is true. The research further supported the importance of a feedback loop of a software system, which is something that company A also wants. The study concludes by proposing suggestions for future studies based on our findings.
